% originally by Sangchul Hahn, and revised by H. Choi

% Acknowledgement Chapter
\clearpage
% \chapter*{Acknowledgement}
\addcontentsline{toc}{chapter}{Acknowledgement}
\thispagestyle{empty}
\begin{center}
    \fontsize{12}{20} \selectfont Acknowledgement
\end{center}
\par

\setstretch{1.5}
First of all, I would like to thank my thesis advisor Prof. Jaechang Nam of the Department of Information and Communication Engineering at Handong Global University. As his first master’s student, I received his full attention and endless advice with his warm heart. Thank you very much for always trying to guide me and respecting me as a researcher. I sincerely respect the professor who waited for me for a long time when I was having a hard time and did his best to guide me without giving up. 

I would also like to thank the committee members of this thesis (Prof. Shin Hong, Prof. Charmgil Hong, and Prof. Jaechang Nam). While they were busy, I would like to thank them for their willingness to serve as a committee member of my dissertation and for their sincere examination of my thesis. 

I would also like to acknowledge every student in ISEL at Handong Global University as the college of my research. Especially, I thank my best friend Sujin Yang for always being with me, whether in joy or sadness.

Finally, I would like to thank my parents and sisters for supporting me to finish my master's degree well. 

\bigskip
\noindent
Author

\noindent
\Author

% End of Acknowledgement Chapter
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
